Detailed disease progression of 97 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis

### 2020-09-22 manuscript/manuscript.Rmd
Cite the new prophylaxis preprint

---
title: "Detailed disease progression of 88 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  #pdf_document
  bookdown::pdf_document2: 
     toc: false
  # bookdown::pdf_book: 
  #    base_format: rticles::arxiv_article
abstract: "We collected a multi-centric retrospective dataset of patients who were admitted to N hospitals in Czech Republic and tested positive for SARS-CoV-2. The dataset contains baseline patient characteristics, breathing support required, pharmacological treatment received and multiple markers on daily resolution. To assess association between treatments, markers and patient outcomes we performed multiverse analysis, observing how the conclusions change between defensible choices of statistical model, predictors included in the model and other analytical degrees of freedom. Additionally we performed external validation of several proposed prognostic models for Covid-19 severity."
bibliography: Covid19.json
date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
---

@@

devtools::load_all()
library(tidyverse)
library(patchwork)
theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
wide <- prepare_marker_data_wide(data)
```

@@

The Covid-19 pandemic, caused by severe acute respiratory syndrome coronavirus (SARS-CoV-2) has, as of September 2020 led to over 28 million cases and over 900 000 deaths. Proposed treatments include antivirals approved for other indications (Chloroquine, Hydroxychloroquine, Lopinavir/Ritonavir, Remdesivir, Favipiravir, Umifenovir), Azithromycin, corticosteriods, immunoglobulins, Tocilizumab and convalescent plasma [@http://zotero.org/users/5567156/items/8XWTUMUI; @http://zotero.org/users/5567156/items/6Q8Z8VJR; TODO]. Currently, the only treatment that exhibited positive effects in randomized trials is the corticosteriod Dexamethasone for severe cases [@http://zotero.org/users/5567156/items/IW6VZ53Q; @http://zotero.org/users/5567156/items/5VAKEW58]. While initially promising, Hydroxychloroquine has failed to show benefit for both hospitalized patients [@http://zotero.org/users/5567156/items/9X3UH8ZM], as early treatment [@http://zotero.org/users/5567156/items/G6KZKVMI] and as post-exposure profylaxis [@http://zotero.org/users/5567156/items/7C23YCV5; @http://zotero.org/users/5567156/items/GMR9FX9Z]. Further, no improvement could be discerned when adding Azithromycin to Hydroxychloroquine therapy [@http://zotero.org/users/5567156/items/BQLRZGTQ]. Similarly, Lopinavir/Ritonavir also did not show benefit [@http://zotero.org/users/5567156/items/6I6GAVWU]. No benefit was observed for convalscent plasma [@http://zotero.org/users/5567156/items/UEXLDJCB; @http://zotero.org/users/5567156/items/BHGT88US] For additional summary see [@http://zotero.org/users/5567156/items/YP62P6XJ].

>>>>

---
title: "Detailed disease progression of 97 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  #pdf_document
  bookdown::pdf_document2: 
     toc: false
  # bookdown::pdf_book: 
  #    base_format: rticles::arxiv_article
abstract: "We collected a multi-centric retrospective dataset of patients who were admitted to N hospitals in Czech Republic and tested positive for SARS-CoV-2. The dataset contains baseline patient characteristics, breathing support required, pharmacological treatment received and multiple markers on daily resolution. To assess association between treatments, markers and patient outcomes we performed multiverse analysis, observing how the conclusions change between defensible choices of statistical model, predictors included in the model and other analytical degrees of freedom. Additionally we performed external validation of several proposed prognostic models for Covid-19 severity."
bibliography: Covid19.json
date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
---

@@

devtools::load_all()
library(tidyverse)
library(patchwork)
theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
wide <- data$marker_data_wide
```

@@

The Covid-19 pandemic, caused by severe acute respiratory syndrome coronavirus (SARS-CoV-2) has, as of September 2020 led to over 28 million cases and over 900 000 deaths. Proposed treatments include antivirals approved for other indications (Chloroquine, Hydroxychloroquine, Lopinavir/Ritonavir, Remdesivir, Favipiravir, Umifenovir), Azithromycin, corticosteriods, immunoglobulins, Tocilizumab and convalescent plasma [@http://zotero.org/users/5567156/items/8XWTUMUI; @http://zotero.org/users/5567156/items/6Q8Z8VJR; TODO]. Currently, the only treatment that exhibited positive effects in randomized trials is the corticosteriod Dexamethasone for severe cases [@http://zotero.org/users/5567156/items/IW6VZ53Q; @http://zotero.org/users/5567156/items/5VAKEW58]. While initially promising, Hydroxychloroquine has failed to show benefit for both hospitalized patients [@http://zotero.org/users/5567156/items/9X3UH8ZM], as early treatment [@http://zotero.org/users/5567156/items/G6KZKVMI], and as both pre- and post-exposure profylaxis [@http://zotero.org/users/5567156/items/7C23YCV5; @http://zotero.org/users/5567156/items/GMR9FX9Z; @http://zotero.org/users/5567156/items/H4CLJNUR]. Further, no improvement could be discerned when adding Azithromycin to Hydroxychloroquine therapy [@http://zotero.org/users/5567156/items/BQLRZGTQ]. Similarly, Lopinavir/Ritonavir also did not show benefit [@http://zotero.org/users/5567156/items/6I6GAVWU]. No benefit was observed for convalscent plasma [@http://zotero.org/users/5567156/items/UEXLDJCB; @http://zotero.org/users/5567156/items/BHGT88US] For additional summary see [@http://zotero.org/users/5567156/items/YP62P6XJ].
